``FISTA'' in Banach spaces with adaptive discretisations

### 2021-10-05 response.tex

\begin{document}
\maketitle

We would like to thank both the reviewers for their time and feedback. All changes are marked in the supplementary pdf and a detailed response to each reviewer is given below.

\section{Detailed response to first reviewer}

\begin{enumerate}
	\item \review{The authors base much of the analysis on the objective function and its convergence properties \ldots it would be interesting to know how the solutions $u_n$ converge for the various versions of FISTA.}

	We thank the reviewer for their suggestion but it seems quite challenging to make a general statement. As in your comment, if one has coercivity then the convergence is clear. Similarly, if one has compact sub-levelsets (e.g. LASSO), then one has convergence of a sub-sequence.

	In the general Hilbert space setting we know FISTA iterates converge weakly (for certain variants). The same result is likely to hold with our adaptivity when the minimiser is in $\F H$, although we haven't verified this special case. The standard proof (e.g. [10]) relies on the bound $\lVert u_n-u_{n-1}\rVert = o(n^{-1})$, i.e. vanishing stepsize in the Hilbert norm, but in general we only expect this quantity to be bounded. It's not clear whether we can adapt the argument to gain any convergence in the Banach space.

### 2021-10-05 paper.tex
edited response

	Without loss of generality we will assume $L=1$, i.e. $\nabla\op{f}$ is 1-Lipschitz. To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
	\begin{equation}
		\norm{\nabla\op{f}(\varf0)- \nabla\op{f}(\varf1)} \leq \norm{\varf0-\varf1}
	\end{equation}
	for all $\varf0,\varf1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
	\begin{equation}
		\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \op{g}(\varf0)
	\end{equation}
	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$. \edit{}{Note in particular we need the argmin to be non-empty. For this we will assume $\spcf0^n$ are locally compact, for example finite dimensional.}

@@

	\subsection{Computing the convergence bound}
	For Step~\ref{step: step 1 stability} of Section~\ref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for Algorithm~\ref{alg: refining FISTA}. The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely. 
	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
	\begin{equation}\label{eq: refining subspace definition}
		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{where }\spcf0^n\text{ is a closed, convex, locally compact subset for all } n\in\F N.
	\end{equation}}

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing. Therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&\leq \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
		\\&\leq\edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2} + \norm{\A(\varf2-\varf0^*)}_{\ell^2}\right]}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant. For the second term, recall $\Norm{\varf2}\leq \Norm{\varf0}$, therefore we can bound
	\begin{equation}
	\norm{\A(\varf2-\varf0^*)}_{\ell^2} = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{\A^*\vvarx3}{\varf2-\varf0^*} \leq \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} |\A^*\vvarx3|_{L^\infty}\Norm{\varf2-\varf0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\varf0}+\Norm{\varf0^*}).
	\end{equation}
	Similarly, the final term can be approximated by
	\begin{multline}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{multline}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}.
		\end{equation}}

>>>>

	Without loss of generality we will assume $L=1$, i.e. $\nabla\op{f}$ is 1-Lipschitz. To get the general statement of any of the results which follow, replace $\op{E}$ with $\frac{\op{E}}{L}$.\edit{ A more important distinction is to say that the properties of $\op{f}$ and $\op{g}$ are stated with respect to the Hilbert norm.}{} In particular,
	\begin{equation}
		\norm{\nabla\op{f}(\varf0)- \nabla\op{f}(\varf1)} \leq \norm{\varf0-\varf1}
	\end{equation}
	for all $\varf0,\varf1\in\F H$ and $\op{g}$ is called `simple' if \edit{}{it is proper, convex, weakly lower-semicontinuous, and}
	\begin{equation}
		\argmin_{\varf0\in\tilde{\spcf0}}\tfrac12\norm{\varf0-\varf1}^2 + \op{g}(\varf0)
	\end{equation}
	is exactly computable for all $\varf1\in\F H$ and all $\tilde{\spcf0}\in\{\spcf0^n\}_{n=0}^\infty$. \edit{}{Closed subsets of $\F H$ are locally weakly compact, therefore this argmin is always non-empty.}

@@

	\subsection{Computing the convergence bound}
	For Step~\ref{step: step 1 stability} of Section~\ref{sec: recipe} we look to replicate the classical bound of the form in \eqref{eq: classical FISTA} for Algorithm~\ref{alg: refining FISTA}. The proofs in this step follow the classical arguments \cite{Beck2009,Chambolle2015} very closely. 
	\edit{}{Throughout this section we consider a sequence $(\spcf0^n)_{n\in\F N}$ which generate the iterates $(\varf0_n)_{n\in\F N}$ in Algorithm~\ref{alg: refining FISTA} such that
	\begin{equation}\label{eq: refining subspace definition}
		\varf0^{n-1}\in\spcf0^n\subset\F H \quad\text{where }\spcf0^n\text{ is a closed, convex subset for all } n\in\F N.
	\end{equation}}

@@

	Application of Theorem~\ref{thm: generic a_U and a_E} gives $\vars3_{\Varf0}=2^{\frac d2}$ although \edit{although}{} $\Norm\cdot$ is too strong a metric and results in $\vars3_{\op{E}}=2^0$. This can be seen because for any $\varf0\in L^1(\Domain)$ and Dirac mass $\delta$ supported in $(0,1)^d$, 
	\begin{equation}
		\Norm{\varf0-\delta} = \sup_{\vard0\in C(\Domain), \norm{\vard0}_{L^\infty}\leq 1} \IP{\vard0}{\varf0-\delta} = \Norm{\varf0}+\Norm{\delta} \geq 1 = \meshsize^0.
	\end{equation}
	To improve our estimate of $\vars3_{\op{E}}$ requires additional assumptions on $\A$. \edit{}{Note that the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\F H\to\tilde{\spcf0}^k$ onto piecewise-constant functions is $\Norm\cdot$-diminishing, therefore }
	for any $\varf0\in\F H$, $\varf2\coloneqq \tilde{\tens{\Pi}}_k\varf0\in\tilde{\spcf0}^k$ we have
	\begin{align}
		\op{E}(\varf2)-\op{E}(\varf0) &= \edit{\tfrac12\norm{\A\varf2-\data}_{\ell^2}^2 - \tfrac12\norm{\A\varf0-\data}_{\ell^2}^2}{\op{f}(\A\varf2-\data)-\op{f}(\A\varf0-\data)} + \mu\left(\Norm{\varf2}-\Norm{\varf0}\right)
		\\&\leq \ip{\nabla \op{f}(\A\varf2-\data)}{\A(\varf2-\varf0)}
		\\&\leq\edit{\max(\norm{\A\varf2-\data}_{\ell^2},\norm{\A\varf0-\data}_{\ell^2})}{\left[\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2} + \norm{\A(\varf2-\varf0^*)}_{\ell^2}\right]}\norm{\A(\varf2-\varf0)}_{\ell^2}.
	\end{align}
	\edit{Choosing $\varf2 = \tilde{\tens{\Pi}}_k\varf0^*$ for any bounded linear extension to the orthogonal projection $\tilde{\tens{\Pi}}_k\colon\spcf0\to\tilde{\spcf0}^k$ gives
	\\\centerline{$\displaystyle\op{E}(\varf2)-\op{E}(\varf0^*) \lesssim \norm{\A(\tilde{\tens{\Pi}}_k\varf0^*-\varf0^*)}_{\ell^2} \leq \norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty}\Norm{\varf0^*}.$}
	Expanding the operator norm further,
	\\\centerline{$\displaystyle
		\norm{(\tilde{\tens{\Pi}}_k-\id)\A^*}_{\ell^2\to L^\infty} = \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain} \frac{|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|}{\norm{\vvarx3}_{\ell^2}} \leq \sup_{\vvarx3\in\R^m} \frac{\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}}{\norm{\vvarx3}_{\ell^2}} 
		= \sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1}$}
	}{Clearly $\norm{\nabla\op{f}(\A\varf0^*-\data)}_{\ell^2}$ is a constant. For the second term, recall $\Norm{\varf2}\leq \Norm{\varf0}$, therefore we can bound
	\begin{equation}
	\norm{\A(\varf2-\varf0^*)}_{\ell^2} = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{\A^*\vvarx3}{\varf2-\varf0^*} \leq \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} |\A^*\vvarx3|_{L^\infty}\Norm{\varf2-\varf0^*} \leq |\A^*|_{\ell^2\to C^0}(\Norm{\varf0}+\Norm{\varf0^*}).
	\end{equation}
	Similarly, the final term can be approximated by
	\begin{multline}
		\norm{\A(\tilde{\tens{\Pi}}_k\varf0-\varf0)}_{\ell^2}
		 = \sup_{\vvarx3\in\R^m}\norm{\vvarx3}_{\ell^2}^{-1} \IP{(\tilde{\tens{\Pi}}_k-\id)\A^*\vvarx3}{\varf0}
		\leq \sup_{\vvarx3\in\R^m}\max_{\vvarx0\in\Domain}|[\tilde{\tens{\Pi}}_k\A^*\vvarx3](\vvarx0)-[\A^*\vvarx3](\vvarx0)|\:\norm{\vvarx3}_{\ell^2}^{-1}\Norm{\varf0}
		\\\leq \sup_{\vvarx3\in\R^m}\sqrt{d}2^{-k}\norm{\nabla[\A^*\vvarx3]}_{L^\infty}\: \norm{\vvarx3}_{\ell^2}^{-1} \Norm{\varf0}\quad=\sqrt{d}2^{-k}|\A^*|_{\ell^2\to C^1} \Norm{\varf0}
	\end{multline}}
	where $\sqrt d2^{-k}$ is the diameter of a $d$ dimensional pixel of side length $2^{-k}$. \edit{}{Sub-levelsets of $\op{E}$ are compact in $L^1(\Domain)$, therefore there exists a weak$^*$-converging minimising sequence $\varf0^*_j\in\F H$ such that $\varf0^*_j\rightharpoonup\varf0^*$ and $\lim_{j\to\infty}\op{E}(\varf0^*_j)=\op{E}(\varf0^*)$. 
		Combining these estimates gives 
		\begin{equation}
			\inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0^*) = \lim_{j\to\infty} \inf_{\varf2\in\tilde{\spcf0}^k} \op{E}(\varf2)-\op{E}(\varf0_j^*) \leq \lim_{j\to\infty} \op{E}(\tilde{\tens{\Pi}}_k\varf0_j^*)-\op{E}(\varf0_j^*) \lesssim 2^{-k}.
		\end{equation}}
